Difference-in-Differences with Spatial Spillovers

### 2023-02-26 latex/slides/Spillover_slides.tex
Slides draft from 2021

\documentclass[aspectratio=169]{beamer}

@@

    Estimation is complicated by \textbf{Spillover Effects}

    \vspace{5mm}
    \textbf{Spillover effects} occur when the effect of treatment extends over the treatment boundaries (states, counties, etc.). Example: Amazon Shipping Center

@@

        \item Having nearby counties with shipping centers raises employment and therefore reduces the effect of \textbf{treated counties} through general equilibrium effects
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments commonly found in the literature

        \item Propose an estimation strategy that improves on current practices by being more robust to spillovers

@@

    \begin{itemize}
        \onslide<2->{
            \item {\bf \color{coral} Spillover onto Control Units:}

            Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
        }

        \onslide<3->{
            \vspace{2.5mm}
            \item {\bf \color{kelly} Spillover onto other Treated Units:}

            Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
        }
    \end{itemize}

@@

\begin{frame}{Remove Bias}
    \only<1>{
        \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
    }
    \only<2>{
        \[ 
            y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} +  + \varepsilon_{it}
        \]
    }

    \only<1>{ 
        \[ 
            \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
        \]
    }
    \only<2>{
        \[ 
            \mathbb{E}[\hat{\tau}] = \tau,
        \]
        so long as $\text{Within}_{it}$ contains all the units with spillovers.
    }
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Single Ring - Removes spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-within_example.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Multiple Rings - Improves estimation of spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-rings_example.pdf}
                } 
            \end{center}
    \end{figure}
\end{frame}

@@

            \vspace{2.5mm}
            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers

            \vspace{2.5mm}
            \item `Rings' are able to estimate spillover effects while still removing all bias
        \end{itemize}

@@

\imageframe{../../figures/figure-spill_within.png}

@@

\imageframe{../../figures/figure-spill_within_additive.png}

\begin{frame}{Estimand of Interest}
    \begin{block}{Estimand of Interest:}
    \[ 
        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
    \]
    \end{block}

    \pause
    \vspace{2.5mm}
    \begin{block}{Spillover Effects:}
    \[
        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]}
    \]

    \[ 
        \textcolor{coral}{\tau_{\text{spillover, control}}} = \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
    \]
    \end{block}
\end{frame}

\begin{frame}{Parallel Trends}
    I assume a modified version of the parallel counterfactual trends assumption:

    \vspace{2.5mm}
    \begin{block}{Assumption: {\it Parallel Counterfactual Trends}}
    \begin{align*}
        \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] = \ \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big]
    \end{align*}
    \end{block}

    \vspace{5mm}
    In the \textit{complete absence of treatment }(not just the absence of individual $i$'s treatment):

@@

\begin{frame}{What does Difference-in-Differences identify?}
    With the parallel trends assumption and random assignment of $D_i$, I decompose the difference-in-differences estimate as follows:

    \begin{align*}
        \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
        \pause&= 
        \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
        &\quad + \quad 
        \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
        &\quad - \quad  
        \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}}
    \end{align*}

@@

\begin{frame}{Removing Bias}

    \begin{block}{Assumption: {\it Spillovers are Local}}

@@

\begin{frame}{Removing Bias}
    With assumption that spillovers are local, define $S_it$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).

    Estimation of the following equation:
    \[ 
        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,treat}} S_{it} * D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
    \]

@@

        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects (hence the need for rings).
    \end{itemize}

@@

\begin{frame}{Aside -- Removing ``contaminated'' controls}
    A common solution to the problem of spillover is to re-estimate on a subsample with neighboring control units removed.

    This is not recommended for two reasons:

    \begin{itemize}
        \item Removing control units from the sample decreases precision of the estimates

        \item Spillover effects on treated units will still remain in the estimand. 
    \end{itemize}
\end{frame}

% ------------------------------------------------------------------------------
\section{Estimation of Spillovers}
% ------------------------------------------------------------------------------

\begin{frame}{Robustness to Misspecification}
    Generate data using the following data-generating process with different exposure mappings:

    \[ 
        y_{\it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill,control}} * (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}
    \]

    \begin{itemize}
        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.

        \item Details in the paper, but $\mu_t$ is normally distributed on a linear time trend, $\mu_i$ are normally distributed
    \end{itemize}

    Then, I estimate each data-generating process using (potentially) misspecified $\tilde{h}(\vec{D}, i)$ and report the average estimate bias.
\end{frame}

\begin{frame}{Specifications of $h(\vec{D}, i)$}

    \begin{itemize}
        \item \textit{Within $40/80$mi.}:
        \begin{itemize}
            \item Indicator for nearest treated unit being within $40/80$ miles.
        \end{itemize}

        \item \textit{Within $40/80$mi. (Additive)}: 
        \begin{itemize}
            \item Number of treated units being within $40/80$ miles.
        \end{itemize}

    \end{itemize}

\imageframe{../../figures/figure-spill_within_large.png}
\imageframe{../../figures/figure-spill_within_large_additive.png}

\begin{frame}{Specifications of $h(\vec{D}, i)$}

    \begin{itemize}
        \item \textit{Decay}: 
        \begin{itemize}
            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
        \end{itemize}

        \item \textit{Decay (Additive)}: 
        \begin{itemize}
            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
        \end{itemize}

    \end{itemize}

\imageframe{../../figures/figure-spill_decay.png}
\imageframe{../../figures/figure-spill_decay_additive.png}

\begin{frame}{Specifications of $h(\vec{D}, i)$}

    \begin{itemize}
        \item \textit{Rings}: 
        \begin{itemize}
            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
        \end{itemize}

        \item \textit{Rings (Additive)}: 
        \begin{itemize}
            \item Set of concentric rings. For each ring, number of treated units being within that distance bin
        \end{itemize}
    \end{itemize}

\imageframe{../../figures/figure-spill_ring.png}

\begin{frame}

    \begin{table}[!tb]
        \caption{Bias from Misspecification of Spillovers}
        \label{tab:misspecification}

        \begin{adjustbox}{width = \textwidth, center}
            \begin{threeparttable}
                \begin{tabular}{@{} l rrrrrr @{}}
                    % Head
                    \toprule
                    & \multicolumn{6}{c}{Data-Generating Process} \\
                    \cmidrule{2-7}

                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\

                    % \input{../../tables/misspecification_slides.tex}
                    TWFE (No Spillovers) & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ \\ \midrule
                    \marktopleft{c1}Within 40mi. & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
                    Within 80mi. & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c1}
                    \onslide<2->{
                        \\ \midrule
                        Within 40mi. (Additive) & $0.043$ & $0.221$ & $-0.006$ & $0.177$ & $0.174$ & $0.143$ \\ 
                        Within 80mi. (Additive) & $0.034$ & $0.134$ & $-0.012$ & $-0.009$ & $0.099$ & $-0.010$ \\ \midrule
                        Decay 80mi. & $-0.159$ & $0.070$ & $-0.174$ & $0.014$ & $-0.009$ & $-0.033$ \\ 
                        Decay 80mi. (Additive) & $-0.023$ & $0.148$ & $-0.084$ & $0.019$ & $0.088$ & $-0.008$
                    }
                    \onslide<3->{
                        \\ \midrule
                        \marktopleft{c2}Rings (0-20, 20-30, 30-40) & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c2}\\ 
                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $0.036$ & $0.134$ & $-0.008$ & $-0.008$ & $0.100$ & $-0.009$ 
                    }

                    \\ \bottomrule
                \end{tabular}
            \end{threeparttable}
        \end{adjustbox}
    \end{table}

    \onslide<3->{
        \textbf{Indicator (or set of rings) that captures \emph{all} affected unit removes all bias}
    }
\end{frame}

\begin{frame}{Spillovers as Estimand of Interest}
    Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.

    However, the two other spillover effects are of interest as well:
    \begin{itemize}
        \item $\textcolor{coral}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?

        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on treatment of neighbors? 
    \end{itemize}

    To estimate the spillover effects, we have to parameterize $h(\vec{D}, i)$ function and the potential outcomes function $Y_i(D_i, h(\vec{D}, i))$.
\end{frame}

\begin{frame}{Estimation of Spillover Effects}
    To see which specifications can predict spillover effects well, I estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.

    Then calculate \[ 
        1 - \frac{
                \overbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}^{\text{Mean Square Prediction Error}}
            }{
                \underbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}_{\text{Normalization}}
            }    
    \]

    This gives the proportion of spillovers explained by $\tilde{h}(\vec{D}, i)$

\begin{frame}
    \begin{figure}[tb!]
        \caption{Single Ring - Removes spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-within_example.pdf}
            }
        \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{figure}[tb!]
        \caption{Multiple Rings - Improves estimation of spillover effects}
        \begin{center}
            \resizebox{0.9\textwidth}{!}{
                \includegraphics{../../figures/figure-rings_example.pdf}
                } 
            \end{center}
    \end{figure}
\end{frame}

\begin{frame}
    \begin{table}[!tb]
        \caption{Percent of Spillovers Predicted by Specification}
        \label{tab:misspecification_mspe}

        \begin{adjustbox}{width = \textwidth, center}
            \begin{threeparttable}
                \begin{tabular}{@{} l rrrrrr @{}}
                    % Head
                    \toprule
                    & \multicolumn{6}{c}{Data-Generating Process} \\
                    \cmidrule{2-7}

                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\

                    % \input{../../tables/misspecification_slides.tex}
                    TWFE (No Spillovers) & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ \\ \midrule
                    \marktopleft{c3}Within 40mi. & $99.4\%$ & $25.9\%$ & $85.6\%$ & $38.8\%$ & $59.5\%$ & $56.1\%$ \\ 
                    Within 80mi. & $39.8\%$ & $96.2\%$ & $34.3\%$ & $71.7\%$ & $85.6\%$ & $68.0\%$ \markbottomright{c3}
                    \onslide<2->{
                    \\ \midrule
                        Within 40mi. (Additive) & $85.3\%$ & $21.2\%$ & $99.5\%$ & $40.6\%$ & $52.0\%$ & $60.7\%$ \\ 
                        Within 80mi. (Additive) & $45.8\%$ & $61.8\%$ & $47.2\%$ & $98.4\%$ & $71.0\%$ & $93.6\%$ \\ \midrule 
                        Decay 80mi. & $60.1\%$ & $82.5\%$ & $52.7\%$ & $75.8\%$ & $97.5\%$ & $82.2\%$ \\ 
                        Decay 80mi. (Additive) & $60.7\%$ & $56.9\%$ & $63.8\%$ & $93.5\%$ & $79.0\%$ & $98.7\%$ 
                    }
                    \onslide<3->{
                        \\ \midrule 
                        \marktopleft{c4}Rings (0-20, 20-30, 30-40) & $98.4\%$ & $23.7\%$ & $85.9\%$ & $37.5\%$ & $58.9\%$ & $56.2\%$ \\ 
                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $96.6\%$ & $91.7\%$ & $84.2\%$ & $72.7\%$ & $91.9\%$ & $78.4\%$ \\ 
                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $83.5\%$ & $57.4\%$ & $97.6\%$ & $95.0\%$ & $73.5\%$ & $94.9\%$\markbottomright{c4} 
                    }

                    \\ \bottomrule
                \end{tabular}
            \end{threeparttable}
        \end{adjustbox}
    \end{table}

    \onslide<3->{
        \textbf{Donuts perform best at estimating spillover effects.}

        \textbf{It is important to get Additive vs. Non-Additive correct.}
    }
\end{frame}

@@

    \pause
    Research Questions:
    \begin{itemize}
        \item What are the local effects of TVA on manufacturing and agricultural economies?
        \item Do these effects come at the cost of other counties?
    \end{itemize}
\end{frame}

@@

\begin{frame}{Controlling for Spillovers in Staggered Treatment Timing}
    \[ 
        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} + \varepsilon_{it}
    \]

@@

    1. Estimate $\mu_i$ and $\mu_t$ using observations that aren't yet treated/affected by spillovers ($D_{it} = 0$ and $Within_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.

    2. Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}}$ (or interacted event study leads/lags). This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).

@@

\begin{frame}{Community Health Centers}
    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974

    \textbf{Research Question:} Do low-/no-cost health services lower the mortality rate of the treated counties? \emph{New Question:} Do these effects spread to neighboring counties?
\end{frame}

>>>>

\documentclass[aspectratio=169,t]{beamer}

@@

    Estimation is complicated by \textbf{Spillover Effects}, when the effect of treatment extends over the treatment boundaries (states, counties, etc.).

    Example: Amazon Shipping Center on employment

@@

        \item Having nearby counties with shipping centers raises wages and therefore reduces the employment effect on \textbf{treated counties}
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item Present a potential outcomes framework to formalize treatment and spillover effects and discuss potential estimands of interest

        \item Discuss estimation of effects that are \emph{robust} to spillovers

@@

    \begin{itemize}
        \onslide<2->{
            \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends
        }

        \onslide<3->{
            \vspace{2.5mm}
            \item {\bf \color{kelly} Spillover onto other Treated Units:} Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
        }
    \end{itemize}

@@

% \begin{frame}{Remove Bias}
%     \only<1>{
%         \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
%     }
%     \only<2>{
%         \[ 
%             y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} +  + \varepsilon_{it}
%         \]
%     }

%     \only<1>{ 
%         \[ 
%             \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
%         \]
%     }
%     \only<2>{
%         \[ 
%             \mathbb{E}[\hat{\tau}] = \tau,
%         \]
%         so long as $S_{it}$ contains all the units with spillovers.
%     }
% \end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Single Ring - Removes spillover effects}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-within_example.pdf}
%             }
%         \end{center}
%     \end{figure}
% \end{frame}

% \begin{frame}
%     \begin{figure}[tb!]
%         \caption{Multiple Rings - Improves estimation of spillover effects}
%         \begin{center}
%             \resizebox{0.9\textwidth}{!}{
%                 \includegraphics{../../figures/figure-rings_example.pdf}
%                 } 
%             \end{center}
%     \end{figure}
% \end{frame}

@@

            \vspace{2.5mm}
            \item Discuss estimands of interest and classify which are identifiable and which are not
        \end{itemize}

@@

@@

\begin{frame}{Estimands}{Treatment Effect without Spillovers}
    \[
        \tau \equiv \mathbb{E} \left[ Y_i(1) - Y_i(0) \mid D_i = 1\right]
    \]
    \vspace{5mm}

    \begin{itemize}
        \item The average effect of switching on unit $i$'s treatment
    \end{itemize}

    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Switching Effect}
    \[
        \textcolor{maroon}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
    \]

    \vspace{5mm}

    \begin{itemize}
        \item Keep everyone's treatment constant and toggle unit $i$'s treatment effect. Average across all units with exposure $h$.

        \item This is policy relevant: what will happen if my county turns on treatment.
        \pause

        \item This requires knowledge of $h_i(\vec{D})$ in order to find control units to estimate $Y_{i1}(0, h_i(\vec{D}))$.
    \end{itemize}

    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Switching Effect}
    \begin{align*}
        \textcolor{maroon}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]} 
    \end{align*}

    \vspace{5mm}
    Identification requires two things:
    \begin{enumerate}
        \item Knowledge of $h_i(\vec{D})$ in order to estimate the second term with control units.

        \item Spillover effect homogeneity (so second term would be the same for treated units).
    \end{enumerate}
    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Total Effect}
    \[
        \textcolor{navy}{\tau_{\text{total}}} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right]
    \]

    \vspace{5mm}
    \begin{itemize}
        \item Toggle entire vector of treatment effects. Average across all treated units.

        \item This is helpful for post-hoc policy analysis: what was the average effect on treated units of implementing $\vec{D}$.
    \end{itemize}

    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Total Effect}
    \begin{align*}
        \textcolor{navy}{\tau_{\text{total}}} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1\right]\\ 
        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]} 
    \end{align*}

    \vspace{5mm}
    Identification much simpler:
    \begin{itemize}
        \item Need to identify control units without spillover effects
    \end{itemize}
    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Direct Effect}
    \[
        \textcolor{kelly}{\tau_{\text{direct}}} \equiv \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right]
    \]

    \vspace{5mm}
    \begin{itemize}
        \item Toggle treatment effect for individuals with no exposure.

        \item This is the switching effect with $h = 0$.

        \pause
        \item Identified under mild assumptions.
    \end{itemize}

    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Direct Effect}
    \begin{align*}
        \textcolor{kelly}{\tau_{\text{direct}}} &= \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]\\ 
        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]} 
    \end{align*}

    \vspace{5mm}
    Identification much simpler:
    \begin{itemize}
        \item Need to identify treated/control units without spillover effects
    \end{itemize}
    \vspace{60mm}
\end{frame}

\begin{frame}{Estimands}{Spillover Effects}
    \[
        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]
    \]

    \[ 
        \textcolor{coral}{\tau_{\text{spillover, control}}} \equiv \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]
    \]
    \vspace{5mm}
    \vspace{60mm}
\end{frame}

\begin{frame}{What does Difference-in-Differences identify?}{Parallel Trends}
    I assume a modified version of the parallel counterfactual trends assumption:

    \vspace{2.5mm}
    \begin{block}{Assumption: {\it Parallel Counterfactual Trends}}
        \vspace{-5mm}
        \begin{align*}
            \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] = \ \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big]
        \end{align*}
    \end{block}

    In the \emph{complete absence of treatment} (not just the absence of individual $i$'s treatment):

@@

\begin{frame}{What does Difference-in-Differences identify?}{Decomposition}
    With the parallel trends assumption, I decompose the difference-in-differences estimate as follows:

    \begin{align*}
        \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
        \pause&= \tau_{\text{direct}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}} \\[3mm]
        \pause&= \tau_{\text{total}} - \textcolor{coral}{\tau_{\text{spillover, control}}} 
    \end{align*}

@@

\begin{frame}{Identification of Direct/Total Effects}
    \begin{block}{Assumption: {\it Spillovers are Local}}

@@

\begin{frame}{Identification of Total Effect}
    With assumption that spillovers are local, define $S_{it}$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).

    \vspace{5mm}
    Estimation of the following equation:
    \[ 
        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
    \]

    \begin{itemize}
        \item $\hat{\tau}$ is consistent for $\tau_{\text{total}}$

        \item $\hat{\tau}_{\text{spill, control}}$ is not consistent for average spillover effects. 
    \end{itemize}
\end{frame}

\begin{frame}{Identification of Direct Effect}
    With assumption that spillovers are local, define $S_{it}$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).

    \vspace{5mm}
    Estimation of the following equation:
    \[ 
        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,treat}} S_{it} * D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
    \]

@@

        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects.
    \end{itemize}

@@

@@

    \pause
    Research Questions:
    \begin{itemize}
        \item What is the total effect of TVA investments on manufacturing and agricultural employment?
        \item Do these effects come at the cost of other counties?
    \end{itemize}
\end{frame}

@@

\begin{frame}{Controlling for Spillovers in Staggered Treatment Timing}
    \[ 
        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} + \varepsilon_{it}
    \]

@@

    1. Estimate $\mu_i$ and $\mu_t$ using observations that are not yet treated/affected by spillovers ($D_{it} = 0$ and $S_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.

    2. Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}}$ (or interacted event study leads/lags). This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).

@@

\begin{frame}{Community Health Centers}
    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974.

    \vspace{5mm}
    Research Question:

    \begin{itemize}
        \item Do low-/no-cost health services lower the mortality rate of the treated counties? 
        \item \emph{New Question:} Do these effects spread to neighboring counties?
    \end{itemize}
\end{frame}
